### 2018-06-21 Thesis/Parts/Research_results/Research_results.tex
journal plots embedded in thesis

\clearpage
\subheader{F1-Score}
Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_avg_f1}
\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
\end{figure}
\begin{figure}[htb]
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
\end{figure}
\clearpage
\subheader{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
\hline
tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
\hline
tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
\hline
\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
\hline
embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
\hline
5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
\hline
10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
\hline
\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
\hline
1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
\hline
\end{tabular}
\end{center}
\caption{Memory usage and performance for each set}\label{table:memoryUsage}
\end{table}

\end{document}

%1k_6k_embedding
%  7.85534550616

%tfidf_embedding
%  9.33435128732

%tfidf_5k_5K
%  10.1820853794

%embedding
%  9.24083300477

%tfidf_5K_10K
%  11.0842682533

%tfidf_10K_10K
%  11.3222696154

%10k_embedding
%  8.75583800194

%5k_embedding
%  8.36120161582

>>>>

\clearpage
\subheader{F1-Score}
Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_avg_f1}
\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
\end{figure}
\begin{figure}[htb]
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
\end{figure}
\clearpage
\subheader{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
\hline
tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
\hline
tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
\hline
\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
\hline
embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
\hline
5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
\hline
10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
\hline
\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
\hline
1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
\hline
\end{tabular}
\end{center}
\caption{Memory usage and performance for each set}\label{table:memoryUsage}
\end{table}
\subheader{Journal relatedness plot}
Figure~\ref{figure:journalPlotNormal} is the two dimensional plot of the journal embeddings. The journals are color-marked by publisher. Red is Wiley, lime is Elsevier and blue is Springer Nature. The grey points are other or not-specified.
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped by a k-means algorithm, creating 8 groups. The bottom right shows the names of the journals closest to the center of the group. The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
\begin{landscape}
\begin{figure}
\includegraphics[height=6.5in]{Plots/journal_plot_normal}
\caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\includegraphics[height=6.5in]{Plots/journal_plot_grouped}
\caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}
\end{figure}
\end{landscape}
\end{document}
